---
title: "Shiny App - plotting and fitting 'swiss' data"
author: "Ivy Woo"
date: "24 January, 2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App functions

This is a simple app which generates a scatter plot on data from the 'swiss' dataset in R.

In the app UI, select a variable as the independent variable and another one
as the dependent variable, a scatter plot of the two variables will be displayed.

A linear regression can be fitted by checking the relevant box.
The regression line will be added to the plot, the regression coefficients 
together with the R-squared value will be provided.

## 'swiss' dataset

The app uses data from the 'swiss' dataset which has 6 variables. All 6 variables
are available as the choice of independent/dependent variable in the app.

Below is how the 'swiss' dataset looks like:

<div style="font-size: 0.8em;">
```{r, echo=TRUE, comment=NA}
head(swiss)
```
</div>

## Scatter plot

Here is an example of the scatter plot that will be generated, where
'Agriculture' is chosen as the independent variable and 'Fertility' as the 
dependent variable.

```{r, fig.align='center', fig.width=6, fig.height=4.5}
plot(swiss$Agriculture, swiss$Fertility, col="blue", pch=16,
     xlab="Agriculture", ylab="Fertility")
grid()
```

Upon checking the linear regression box, the regression line (in red) will be shown 
in the plot, the regression coefficients and the R-squared value will be given below the plot.

***
<br>
<br>
<br>
<br>
<br>
<br>
<center>
Thank you! Have fun in playing around with the app :)
</center>

